### 2014-12-12 paper.tex
Add scatterplots to paper

>>>>

  \begin{figure}
    \begin{center}
      \includegraphics[width=0.49\textwidth]{sss-area_per.pdf}
      \includegraphics[width=0.49\textwidth]{sss-convex_hull.pdf}

      \includegraphics[width=0.49\textwidth]{sss-convex_hull_pop.pdf}
      \includegraphics[width=0.49\textwidth]{sss-moment_area.pdf}

      \includegraphics[width=0.49\textwidth]{sss-moment_pop.pdf}
      \parbox[b][3in][c]{0.49\textwidth}{\caption{Plots of efficiency gap (as computed by seat share, in seats) against each compactness metric.\label{f:compactnessplots}}}
    \end{center}
  \end{figure}

  \begin{figure}
    \begin{center}
      \includegraphics[width=0.49\textwidth]{sss-moment_pop.pdf}
      \includegraphics[width=0.49\textwidth]{wvs-moment_pop.pdf}

      \includegraphics[width=0.49\textwidth]{ssp-moment_pop.pdf}
      \includegraphics[width=0.49\textwidth]{wvp-moment_pop.pdf}

      \caption{Plots of each efficiency gap computation against each compactness as measured by moment of population.\label{f:effgapplots}}
    \end{center}
  \end{figure}
